\documentclass[a4paper]{article}

\usepackage{fullpage} % Package to use full page
\usepackage{parskip} % Package to tweak paragraph skipping
\usepackage{tikz} % Package for drawing
\usepackage{amsmath}
\usepackage{hyperref}

\title{CSCI 33500 Software Analysis and Design 3}
\author{Instructor: Jaime Canizales}
\date{Monday - Thursday, West Bldg W207, Spring 2024}

\begin{document}
\maketitle

\textbf{Textbook:} Data Structures \& Algorithm Analysis in C++, 4th Edition. Mark Allen Weiss. Pearson, New
York. ISBN: 013284737x.
\\\\
\textbf{Email:} jaime.canizales@hunter.cuny.edu \\
\textbf{Office Hours:} By appointment.

\textbf{Course Description:}\\ The principal objective of this course is to further your understanding of the design and analysis of
algorithms and data structures. This includes the introduction of new abstract data types, including
hashes, heaps, various forms of trees, graphs, and the sorting problem from a higher perspective than
was [supposed to be] presented in CSci 235. It also covers worst and average case behavior analysis
and optimality, and to a much smaller extent, polynomial time complexity classes and theory. Another
objective of the course is to develop your C++ programming and software engineering skills a little more.
This course requires that you write more complex software than you have done in the preceding courses.

\textbf{Grading: } \\
Midterm Exam: \hspace{1mm} 30\% \\
Final Exam: \hspace{6mm} 30\% \\
Project: \hspace{13mm} 40\%
\\\\
\textbf{Exams:} There will be one midterm and a final. The first midterm will cover the first five chapters of
the textbook. The final will cover chapters six to nine. These chapters are not covered in their entirety,
check notes to reviews topics covered from chapters.\\

\textbf{Projects: } There will be three assignments, which will be posted on blackboard.

\textbf{Hunter College Official Policies:}\\
Hunter College regards acts of academic dishonesty (e.g., plagiarism, cheating on examinations, obtaining
unfair advantage, and falsification of records and official documents) as serious offenses against the values of
intellectual honesty. The college is committed to enforcing the CUNY policy on Academic Integrity and will
pursue cases of academic dishonesty according to the Hunter College Academic Integrity Procedures.
\par In compliance with the American Disability Act of 1990 (ADA) and with Section 504 of the Rehabilitation
Act of 1973, Hunter College is committed to ensuring educational parity and accommodations for all students
with documented disabilities and/or medical conditions. It is recommended that all students with documented
disabilities (Emotional, Medical, Physical and/or Learning) consult the Office of AccessABILITY located in
Room E1124 to secure necessary academic accommodations. For further information and assistance please call
(212-772-4857)/TTY (212-650-3230)
\end{document}